Long term cloud enhancement events of global solar irradiance over Thessaloniki

### 2024-06-06 article/article.tex
Commit 2024-06-07 00:17

{\centering \includegraphics[width=1\linewidth]{../images/P_CS_change-1}

@@

{\centering \includegraphics[width=1\linewidth]{../images/P_energy-7}

@@

{\centering \includegraphics[width=1\linewidth]{../images/P_energy-6}

@@

{\centering \includegraphics[width=1\linewidth]{../images/P_energy-5}

@@

{\centering \includegraphics[width=1\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}

@@

{\centering \includegraphics[width=1\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}

@@

{\centering \includegraphics[width=1\linewidth]{../images/example_days-18}

@@

{\centering \includegraphics[width=1\linewidth]{../images/example_years-13}

>>>>

{\centering \includegraphics[width=1\linewidth]{../images/P-CS-change-1}

@@

{\centering \includegraphics[width=1\linewidth]{../images/P-energy-3}

@@

{\centering \includegraphics[width=1\linewidth]{../images/P-energy-2}

@@

{\centering \includegraphics[width=1\linewidth]{../images/P-energy-1}

@@

{\centering \includegraphics[width=1\linewidth]{../images/clim-CE-month-norm-MAX-median-N-1}

@@

{\centering \includegraphics[width=1\linewidth]{../images/clim-ECE-month-norm-MAX-median-N-2}

@@

{\centering \includegraphics[width=1\linewidth]{../images/example-days-18}

@@

{\centering \includegraphics[width=1\linewidth]{../images/example-years-13}
